\documentclass[letterpaper,11pt]{letter}
\usepackage{graphicx}
\usepackage{lipsum}
\usepackage{geometry}
\usepackage{fontawesome5}
\usepackage{hyperref}
\geometry{top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm}
\setlength{\parskip}{0.5em}
\thispagestyle{empty}
\begin{document}
\begin{center}
    \textbf{\Huge Mohaddeseh Mozaffari} \\
    \small{\href{mailto:mohaddeseh.mozaffarii@gmail.com}{\faIcon{envelope} mohaddeseh.mozaffarii@gmail.com} | 	\href{https://www.linkedin.com/in/MohiMozaffari/}{\faIcon{linkedin} MohiMozaffari}}
\end{center}

\vspace{1em}

\begin{flushleft}
    MILA Admissions Committee\\
    6666 Saint-Urbain Street, Suite 200\\
    Montreal, QC, H2S 3H1\\
    \texttt{info@mila.quebec} \\
    December 1, 2024
\end{flushleft}

\vspace{1em}

\begin{flushleft}
    Dear MILA Admissions Committee,
\end{flushleft}

\vspace{1em}
I am very interested in joining MILA because of my strong background in physics and complex systems, as well as my passion for interdisciplinary fields, cognitive science, data science, and medicine. Attending various seminars and workshops has deepened my interest in these areas, and I believe MILA provides the perfect environment for me to meet and collaborate with professors and experts from diverse fields related to artificial intelligence. This would not only allow me to engage with academic research but also to immerse myself in a new and inspiring environment full of hardworking people in the AI community.

Currently, I am completing my Master's degree at Shahid Beheshti University, where I am working on fMRI data analysis using Topological Data Analysis (TDA). In addition, I am collaborating on a project focused on segmenting X-ray angiography data. These experiences have allowed me to apply machine learning and AI techniques to real-world data, which has been very insightful. I also have a strong programming background in Python, C++, and Git, and I love sharing my code on GitHub to learn from others and help others benefit from my work. To further share my knowledge, I also teach Python programming, which has helped me refine my ability to explain complex concepts in an accessible way to individuals with different backgrounds.

I believe MILA offers an exceptional opportunity for me to work on a wide range of topics. By combining my background in physics, programming, and medical research, I aim to contribute to solving societal problems, particularly in the field of brain science. Having ADHD myself, I have experienced firsthand how much medicine and research can improve quality of life. This has inspired me to help others, particularly in areas that are not yet well-understood or where challenges remain, and I hope to use my skills to make a meaningful impact in these fields.

Additionally, some professors at MILA collaborate with other universities across Canada, including those in different cities like Toronto. This would give me the chance to explore other parts of Canada and become familiar with different cultures. Being in Montreal, a bilingual city, would also provide an excellent opportunity for me to improve my French language skills.

I believe that being at MILA will allow me to engage in a creative and innovative academic environment and to form new collaborations in the field of artificial intelligence.

Thank you very much for considering my application. I hope to have the opportunity to work with MILA and contribute my skills and knowledge to the institute.



\begin{flushleft}
    Sincerely, \\
    \textbf{Mohaddeseh Mozaffari}
\end{flushleft}

\end{document}


